\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-19 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section IV

Notice that \eqref{XiEtaVectorSDE} is a mixed conservative-dissipative SDE with \emph{isotropic} degenerate diffusion. In particular, the pushforward of the known initial joint PDF \eqref{FPKInitCond} via $\bm{\Psi}$, is given by
\begin{align}
\tilde{\rho}_{0}(\bm{\xi},\bm{\eta}) := \bm{\Psi}_{\sharp} \rho_{0} 
&= \dfrac{\rho_{0}\left(\bm{\Psi}^{-1} \begin{pmatrix}
\bm{\xi}\\
\bm{\eta}	
\end{pmatrix}\right)}{|\det\left(\bm{\Psi}\right)|} \nonumber\\
&= \dfrac{\rho_{0}\left(\bm{\Sigma}\bm{M}^{-1}\bm{\xi},\bm{\Sigma}\bm{M}^{-1}\bm{\eta}\right)}{\left(\displaystyle\prod_{i=1}^{n}m_{i}/\sigma_{i}\right)^{\!2}},
\label{PushforwardOfIC}	
\end{align}
where we used the standard properties of the Kronecker product. The transient joint state PDF $\tilde{\rho}(t,\bm{\xi},\bm{\eta})$ corresponding to \eqref{XiEtaVectorSDE} solves the PDE initial value problem
\begin{subequations}
\begin{align}
&\dfrac{\partial\tilde{\rho}}{\partial t} = -\langle\bm{\eta},\nabla_{\bm{\xi}}\tilde{\rho}\rangle + \nabla_{\bm{\eta}}\cdot\left(\tilde{\rho}\left(\nabla_{\bm{
\xi}}U(\bm{\xi})+\nabla_{\bm{\eta}}F(\bm{\eta})\right)\right) + \dfrac{1}{2}\Delta_{\bm{\eta}}\tilde{\rho}, \label{NewPDE}\\
&\tilde{\rho}(t=t_{0},\bm{\xi},\bm{\eta}) = \underbrace{\tilde{\rho}_{0}(\bm{\xi},\bm{\eta})}_{\text{from}\;\eqref{PushforwardOfIC}}. \label{NewIC}	
\end{align}
\label{TransformedPDEivp}	
\end{subequations}
In other words, \eqref{TransformedPDEivp} is the macroscopic dynamics corresponding to the sample path dynamics \eqref{XiEtaVectorSDE}.

@@

To numerically perform the proximal updates $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ for $k\in\mathbb{N}$, we implement an instance of the Algorithm 1 in \cite{caluya2019TAC}. This algorithm implements a dualization along
with an entropic regularization of the variational update \eqref{KineticProx}, and then solves the same using a fixed point
recursion that is provably contractive; see \cite[Sec. V.B]{caluya2019TAC}.

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta},\bm{\omega}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi},\bm{\eta}\right) \nonumber\\
&= \left(\prod_{i=1}^{n}m_{i}/\sigma_{i}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}\right).
\label{BringBackOriginalStateSpace}	
\end{align}
The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}.

>>>>

Notice that \eqref{XiEtaVectorSDE} is a mixed conservative-dissipative SDE with \emph{isotropic} degenerate diffusion. In particular, the pushforward of the known initial joint PDF \eqref{FPKInitCond} via $\bm{\Psi}$, is given by
\begin{align}
\tilde{\rho}_{0}(\bm{\xi},\bm{\eta}) := \bm{\Psi}_{\sharp} \rho_{0} 
&= \dfrac{\rho_{0}\left(\bm{\Psi}^{-1} \begin{pmatrix}
\bm{\xi}\\
\bm{\eta}	
\end{pmatrix}\right)}{|\det\left(\bm{\Psi}\right)|} \nonumber\\
&= \dfrac{\rho_{0}\left(\bm{\Sigma}\bm{M}^{-1}\bm{\xi},\bm{\Sigma}\bm{M}^{-1}\bm{\eta}\right)}{\left(\displaystyle\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!2}},
\label{PushforwardOfIC}	
\end{align}
where we used the standard properties of the Kronecker product. The transient joint state PDF $\tilde{\rho}(t,\bm{\xi},\bm{\eta})$ corresponding to \eqref{XiEtaVectorSDE} solves the PDE initial value problem
\begin{subequations}
\begin{align}
&\dfrac{\partial\tilde{\rho}}{\partial t} = -\langle\bm{\eta},\nabla_{\bm{\xi}}\tilde{\rho}\rangle + \nabla_{\bm{\eta}}\cdot\left(\tilde{\rho}\left(\nabla_{\bm{
\xi}}U(\bm{\xi})+\nabla_{\bm{\eta}}F(\bm{\eta})\right)\right) + \dfrac{1}{2}\Delta_{\bm{\eta}}\tilde{\rho}, \label{NewPDE}\\
&\tilde{\rho}(t=t_{0},\bm{\xi},\bm{\eta}) = \underbrace{\tilde{\rho}_{0}(\bm{\xi},\bm{\eta})}_{\text{from}\;\eqref{PushforwardOfIC}}. \label{NewIC}	
\end{align}
\label{TransformedPDEivp}	
\end{subequations}
In other words, \eqref{TransformedPDEivp} is the macroscopic dynamics corresponding to the sample path dynamics \eqref{XiEtaVectorSDE}.

@@

To numerically perform the proximal updates $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ for $k\in\mathbb{N}$, we implement an instance of the Algorithm 1 in \cite{caluya2019TAC}. This involves a dualization along
with an entropic regularization of the variational update \eqref{KineticProx}, and then solving the same using a fixed point recursion that is provably contractive; see \cite[Sec. V.B]{caluya2019TAC}. This enables a nonparametric computation of $\tilde{\varrho}_{k}^{i} \equiv \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)$ for $i=1,\hdots,N$.

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}.
